### 2023-03-01 paper-thesis/chapters/24-backend.tex
Add meeting notes

\todo{finish this after implementing}

@@

Finally, inductive data types are a bit harder to compile, as Clojure does not have an equivalent to sum types on which we can match. \todo{finish this after implementing}

>>>>

\todo{finish this after implementing}
- discuss efficiency (reference "Optimizing first class pattern matching")

@@

-analysis is hard, agda doesn't do it
- if compiled language doesn't matter
- erasure annotations (idris/agda)

Finally, inductive data types are a bit harder to compile, as Clojure does not have an equivalent to sum types on which we can match. \todo{finish this after implementing}
- agda to scheme compiler
- atoms voor constructors
